---
title: "ESM 262 assignment 3- SJKF"
author: "Jessica Copeland"
date: "2025-03-17"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I am recycling my SJKF function with a few improvements, since I am working solo. 

```{r}
# Here is the function I created, which is also saved as a separate R file. 

#' San Joaquin Kit Fox weights and home ranges (an almost correct function)
#'
#' @param W is weight of the fox in pounds. 
#' @param G is gender of the fox. The only options are: 1 for female, 2 for male
#' @param HR_minimum is the minimum home range size of the fox in meters, in this case always 1000. #
#' @returns HR_indiv  The home range for the individual in meters. 


SJKF_range=function(W,G,HR_minimum=1000,HR_indiv) {

  if(W<0) W=NA # Weight should not be less than zero
  
  # Using ifelse() to set NA for values that are not 1 or 2, because we can only have 1 and 2 to specify the genders of the animals. 
  G <-ifelse(G != 1 & G != 2, NA, G)

  #    return("Home range cannot be less than 0")
  if (HR_minimum < 0) return("Home range cannot be less than 0")

  # Calculate the home range of the individual SJKF 
   result <- (W * G) + HR_minimum

return(result)
}

```

 I have this function saved as  # SJKF_func.R #
 
```{r}
# I will bring in the function now

source("C:/Users/jcope/OneDrive/Desktop/UCSB/R/SJKF_func.R")
```
 Let's generate some data using a for loop! 
 
```{r}
# Lets say I want to generate 10 different weights.. 
num_weights <- 10

# I want to create a vector (empty) to store the weights. 
weights <- numeric(num_weights)

# Then I can use a "for loop" to generate random weights
set.seed(123)  # Ensures reproducibility
for (i in 1:num_weights) {
  weights[i] <- runif(1, min = 3, max = 15)  # Generate a random weight
}

# Print the generated weights
print(weights)
```
 Cool that gave me 10 different weights. 
 Now I want to try some more looping with purrr, but I want it to give me whole integers instead. 
```{r}
library(purrr)

set.seed(123)

# Generate 10 random integer weights between 3 and 15
weights <- map_int(1:10, ~ sample(3:15, 1))

print(weights)
```
 
 
 So now that I have weights, I will try and plug each one into the function...
```{r}
#First I want to use these numbers and assume they are all females..
SJKF_range(G=1, W=5)
SJKF_range(G=1, W=5)
SJKF_range(G=1, W=12)
SJKF_range(G=1, W=4)
SJKF_range(G=1, W=8)
SJKF_range(G=1, W=13)
SJKF_range(G=1, W=7)
SJKF_range(G=1, W=6)
SJKF_range(G=1, W=8)
SJKF_range(G=1, W=11)

```
 Now if I do the same thing assuming they are all males.... 
 
```{r}
SJKF_range(G=2, W=5)
SJKF_range(G=2, W=5)
SJKF_range(G=2, W=12)
SJKF_range(G=2, W=4)
SJKF_range(G=2, W=8)
SJKF_range(G=2, W=13)
SJKF_range(G=2, W=7)
SJKF_range(G=2, W=6)
SJKF_range(G=2, W=8)
SJKF_range(G=2, W=11)
```
 
Now that I have inputs and outputs, I can attempt to plot these... 

```{r}
# Females first

# Load ggplot2
library(ggplot2)

# Data from females
data_f <- data.frame(
  Weight = c(5, 5, 12, 4, 8, 13, 7, 6, 8, 11),  # Weights
  HomeRange = c(1005, 1005, 1012, 1004, 1008, 1013, 1007, 1006, 1008, 1011),  # Corresponding home ranges
  Gender= "Female"
)

# Create a scatter plot
ggplot(data_f, aes(x = Weight, y = HomeRange)) +
  geom_point(color = "pink", size = 3) +  # Add points
  labs(
    title = "San Joaquin Kit Fox Weights vs Home Ranges",
    x = "Weight (pounds)",
    y = "Home Range (meters)"
  ) +
  theme_minimal()  # Use a clean theme
```
Well, this ends up being super boring because of how I set up my function, oops! 

I will try the males anyway... 

 
```{r}
# Now males... 

data_m <- data.frame(
  Weight = c(5, 5, 12, 4, 8, 13, 7, 6, 8, 11),  # Weights
  HomeRange = c(1010, 1010, 1024, 1008, 1016, 1026, 1014, 1012, 1016, 1022), # Corresponding home ranges
  Gender="Male"
)

# Create a scatter plot
ggplot(data_f, aes(x = Weight, y = HomeRange)) +
  geom_point(color = "blue", size = 3) +  # Add points
  labs(
    title = "San Joaquin Kit Fox Weights vs Home Ranges",
    x = "Weight (pounds)",
    y = "Home Range (meters)"
  ) +
  theme_minimal()  # Use a clean theme
```
I realized I want to combine my two datasets...

```{r}
# Combine the two datasets..now I can plot beter (hopefully)
data_combined <- rbind(data_m, data_f)
```

 
Now plot!! 

```{r}
ggplot(data_combined, aes(x = Weight, y = HomeRange, color = Gender)) +
  geom_point(size = 3) +  # Add points, color-coded by gender
  labs(
    title = "San Joaquin Kit Fox Weights vs Home Ranges by Gender",
    x = "Weight (pounds)",
    y = "Home Range (meters)"
  ) +
  theme_minimal()
```

 Now I want to try running some tests of my function with the test file...
 
```{r}

library(testthat)

testthat::test_file("C:/Users/jcope/OneDrive/Desktop/UCSB/R/sjkf_test.R")

#remember where you saved that test file!
```
 I got 0 fail, 0 warn, 0 skip, and 8 pass... which means that a total of 8 tests were conducted, and they all passed. 
 
 So my function should be working just fine! 
 